% TEMPLATE for Usenix papers, specifically to meet requirements of
%  USENIX '05
% originally a template for producing IEEE-format articles using LaTeX.
%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
% adapted by David Beazley for his excellent SWIG paper in Proceedings,
%   Tcl 96
% turned into a smartass generic template by De Clarke, with thanks to
%   both the above pioneers
% use at your own risk.  Complaints to /dev/null.
% make it two column with no page numbering, default is 10 point

% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
% the .sty file from the LaTeX source template, so that people can
% more easily include the .sty file into an existing document.  Also
% changed to more closely follow the style guidelines as represented
% by the Word sample file. 

% Note that since 2010, USENIX does not require endnotes. If you want
% foot of page notes, don't include the endnotes package in the 
% usepackage command, below.

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage{listings}

\usepackage{color} % for initialed in-line comments
\usepackage{authblk}  % supports multiple authors
\usepackage[nocompress]{cite} % orders in-line citations by increasing numeric value

\newcommand{\kmd}[1]{{\textcolor{blue}{[[#1 -- kmd]]}}}


\begin{document}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Request Level Fault Injection}

% Standing on the Shoulders of Traces: Request Level Fault Injection

\author{Tuan Tran, Peter Alvaro}
\affil{\textit{University of California, Santa Cruz} \vspace{0.5ex} \authorcr {\tt \{//, palvaro\}@ucsc.edu}\vspace{0.0ex}}

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.

\begin{abstract}
Recent years manifest the growing presence of microservices as the dominating architecture for the modern landscape user-facing applications. Microservice architectures (or simply ``microservices'') are characterized as a thoroughly decentralized, distributed topology of services providers designed to coordinate in response to client requests. Accordingly, given the constant specters of asynchrony and partial failure, the occurrence of potentially devastating fault scenarios is not a question of `if' but `when'. In this paper, we present Request Level Fault Injection (RLFI) as an efficient approach to performing fault injection experiments on large-scale microservice architectures which minimizes disruptions on the critical path. We present a framework allowing developers to trigger faults on microservices at the request level and obtain fine-grained traces of the system for analysis. This work builds upon a popular tracing infrastructure known as OpenTracing\cite{opentracing:doc} to support data propagation over the wire while providing complementary traces of the system in response to fault injection experiments. We describe our motivation for the work, the benefits of adoption, a proof-of-concept implementation, and an evaluation of the framework prior to speculating about a number of future directions.
\end{abstract}


% good sentence: To minimize disruptions on the critical path, fault injection experiments designed to actively challenge the correctness guarantees of distributed systems target critical points of failure in the microservice topology either prior to deployment or during non-peak hours. 


\input{introduction}
\input{background}
\input{implementation}
\input{futureWork}
\input{relatedWork}
\input{conclusion}


\section{Acknowledgments}
We would like to thank Peter Alvaro for the initial suggestion to explore Opentracing for fault injection which materialized this project and the extremely helpful feedback on both design and implementation of the framework. We also thank Nikhil Kini and Kamala Ramasubramanian for the helpful feedback provided as this project was presented and we thank Ashutosh Raina, Kathryn Dahlgren, Sarah Borland, and Asha Karim for making use of the traces for their projects. Last but not least, we thank the team at Netflix and Lightbend for making us realize that our work is very much relevant to their everyday needs in the industry setting.

\bibliographystyle{acm}
\bibliography{sample}

\end{document}







